---
title: "Shiny Application & Reproducible Pitch"
author: "shahivivdhruv"
date: "February 12, 2019"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## The Pitch

#### Box office Return and Gross for Top movies.
 
* The Shiny app allows the user to view the name of the most profitable movies.
The movies can be filtered using interactive slider based on following criteria:

1. Year (From 1920 to 2018)
2. Budget (From 3M to 430 M)
3. Number of data points (minimum 3 to maximum 100)

Also, the user can choose to plot the Gross world-wide or the Return against the budget. 

## Example 1: Plotting GrossWW

#### This screenshot shows the result of selecting top 20 movies from 2000 to 2018 in terms of GrossWW.

```{r, echo = FALSE, message=FALSE, warning = FALSE}
library(dplyr)
library(plotly)

a<-read.csv("filename.csv", sep="," )
a<-subset(a, a$GrossWW>100000, rm.na=TRUE)
a<-mutate(a, "Return"=GrossWW/Budget)
a$Return<-round(a$Return, digits = 2)
a$Budget<-as.numeric(a$Budget)

    b<-subset(a, a[,1]>=2000 & a[,1]<=2018, rm.na=TRUE)
        c<-subset(b, b[,3]>=3000000 & b[,3]<=430000000, rm.na=TRUE)
        budget1<-3000000
        budget2<-430000000
        
        
        if(min(c$Budget)>=budget1){
            budget1<-min(c$Budget)
            }
        
        if(max(c$Budget)<=budget2){
            budget2<-max(c$Budget)
            }
        
        c<-subset(b, b[,3]>=budget1 & b[,3]<=budget2, rm.na=TRUE)
        mini<-length(c[,1])
         
        if(20<=length(c[,1])){mini<-20}
        
        
            c<-c[order(-c$GrossWW),]
            d<-subset(c[1:mini,], rm.na=TRUE)
            plot_ly(d, x = ~Budget, y = ~GrossWW,text= ~paste(Name,"\n","Year:",Year,"\n","Return:", Return), type='scatter',
                    mode='markers', marker=list(size=10,  opacity=0.7))
        

```

## Example 2: Plotting  Return 

#### This screenshot shows the result of selecting top 20 movies from 2000 to 2018 in terms of Return.

```{r, echo = FALSE, message=FALSE, warning = FALSE}
library(dplyr)
library(plotly)

a<-read.csv("filename.csv", sep="," )
a<-subset(a, a$GrossWW>100000, rm.na=TRUE)
a<-mutate(a, "Return"=GrossWW/Budget)
a$Return<-round(a$Return, digits = 2)
a$Budget<-as.numeric(a$Budget)

    b<-subset(a, a[,1]>=2000 & a[,1]<=2018, rm.na=TRUE)
        c<-subset(b, b[,3]>=3000000 & b[,3]<=430000000, rm.na=TRUE)
        budget1<-3000000
        budget2<-430000000
        
        
        if(min(c$Budget)>=budget1){
            budget1<-min(c$Budget)
            }
        
        if(max(c$Budget)<=budget2){
            budget2<-max(c$Budget)
            }
        
        c<-subset(b, b[,3]>=budget1 & b[,3]<=budget2, rm.na=TRUE)
        mini<-length(c[,1])
         
        if(20<=length(c[,1])){mini<-20}
        
        
              c<-c[order(-c$Return),]
            d<-subset(c[1:mini,], rm.na=TRUE)
            plot_ly(d, x = ~Budget, y = ~Return,text= ~paste(Name,"\n","Year:",Year,"\n","Gross:",GrossWW), type='scatter',
                mode='markers', marker=list(size=10, opacity=0.7))
```


## Acknowledgement

The Data has been obtained from the following site:
https://www.the-numbers.com/movie/budgets/all

The shiny application can be found here: https://vivekshahi.shinyapps.io/movies/
